---
title: "Blake Holmes CV"
author: Blake Holmes
date: "`r Sys.Date()`"
params:
  is_pdf:
    value: false
output:
  pagedown::html_resume:
    css: [ 'dd_cv.css', 'custom.css','resume']
    self_contained: true
#knit: pagedown::chrome_print      
---

```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "bjholmes23") %>% 
  meta_social(
    title = "Blake Holmes CV",
    description = paste(
      "Blake Holmes CV"
    ),
    url = "https://blakeholmes.com/index.html",
    og_type = "website",
    og_author = "Blake Holmes"
  )


```
<!-- all links open as new tab -->

<base target="_blank">
<!-- inicio academic icons -->

<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css"> <!-- final academic icons -->

<!-- inicio font awesome -->

```{=html}
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>
```
<!-- final font awesome -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/14nK5Bao8oQrFt1BYpwGn7Wie-AnGl2JRhN2sUcS0_Mg/edit?usp=sharing",  
  is_pdf = params$is_pdf
)

CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$is_pdf) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

```{r}
 if(params$is_pdf){
   cat("<i class='fas fa-download'></i> [View online](https://blakeholmes.com/)")
 } else {
   cat("<i class='fas fa-download'></i> [Download as PDF](https://blakeholmes.com/HolmesB-resume.pdf)")
 }
```


## Contact {#contact}

- <i class="fa fa-phone" style="font-size: 13px;"></i> +1 571 491 1905

- <i class="fa fa-home"></i> [blakeholmes.com](https://blakeholmes.com)

- <i class="fa fa-envelope"></i> [bjholmes`@`pm.me](mailto:bjholmes@pm.me)

- <i class="fa fa-github"></i> [Git`@`bjholmes23](https://github.com/bjholmes23)

- <i class="fa fa-linkedin"  style="font-size: 14px;"></i> [holmesblake](https://www.linkedin.com/in/holmesblake/)

## Certifications {#teachingr}

<i class="fas fa-flag-usa"></i> US Top Secret Clearance

<i class="fas fa-project-diagram"></i> Certified Agile Scrummaster

## Languages {#languages}

**English:** Native

**Chinese:** Intermediate

```{echo, echo=FALSE}
<i class="fab fa-r-project"></i> `R`

<i class="fab fa-python"></i> `Python`

<i class="fas fa-database"></i> `SQL`

<i class="fab fa-windows"></i> `Powershell`

<i class="fab fa-js"></i> `JS/NodeJS`

<i class="fab fa-php"></i> `Laravel`

<i class="fab fa-docker"></i> `Docker`

<i class="fab fa-aws"></i> `AWS`

<i class="fab fa-ubuntu"></i></i> `Ubuntu`}

```

## Tech Skills {#skills}

```{r}
CV %>% print_skill_bars()
```

# Main

## Blake Jungé Holmes {#title}

### aspiring data scientist, software developer, technology leader

<div class="intro">
```{r}
CV %>% print_text_block("opening_statement")
```
</div>

## Current Employment {data-icon="suitcase"}

```{r}
CV %<>% print_section('current_employment')
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Previous Employment {data-icon="laptop"}

```{r}
CV %<>% print_section('employment')
```


```{r}

## Personal Projects {data-icon="chalkboard-teacher"}

#Here is a collection of side projects I've worked on. These were primarily used as learning exercises. 

#CV %<>% print_section('projects')
```
